\huge{DRAFT} \\ ~\\ \Large\bf Data Intensive processing with iRODS and the middleware CiGri for the Whisper project

### 2014-06-13 articles/2014/whisper/aricleEbauche/Draft_BriandBzeznikIrodsUserMeeting2014.tex
change name file, small change shema script for transfer Irods and change jdl

%\end{multicols}
\begin{center}[h]
\centering
\captionof{figure}{\label{whisperCorrelationStep} Step of the correlations}
\includegraphics[width=6cm]{schemaCorrelationStep.png}
\end{center}
%\begin{multicols}{2}

@@

Whisper is one of the projects that have made it possible to ensure that the seismic noise brought new observable.
This permits to carry out several scientific results including imaging and monitoring. 
Concerning monitoring, further studies provide news results about sligth variations of seismics waves induce by earthquakes.
Many articles are in part due to this project as well as
several post-docs and PhD (see \cite{key:CFLC2010, key:BPCPBR, key:HCM2014, key:OPLC2013, key:PCP}) and also whisper.obs.ujf-grenoble.fr, rubric publication).

@@

@@

For each of the 1280 jobs, a script is launched by CiGri , say 'start.bash', that take for
arguments a line of the file parameter. The script, among other things, load necessary library like appropriate python, retrieve the code on iRODS,
here 'main.py' and run the code (This is a diagrammatic view).

@@

#!/bin/bash
set -e
...
module load python
...
DirToCompute=$1
cd DirToCompute
...
iget -rf Codes
cd Codes
...
NumberDate=$2
IndexDate=$3
NumberStation=$4
IndexStation=$5
...
python main.py NumberDate 
     IndexDate NumberStation IndexStation
...
cd
rm -rf DirToCompute
\end{lstlisting}

@@

  "clusters": {
    "c1": {
       	"prologue": [
       	secure_iget -f /IrodsColl/start.bash,
       	secure_iget -f /IrodsColl/param.txt,
       	... other lines of commands ],
       	"project": "whisper",
       	"walltime": "00:20:00"
       	},
    "c2": {
    	"prologue": [
        ... lines of commands ],
        "project": "whisper",
        "max_jobs": "450",
        "walltime": "00:30:00"
    	},
    ...
    }
...
}
\end{lstlisting}

Here the campaign named 'test\_processing' take only one core. It run the file 'start.bash' with the parameter
file 'param.txt' in mode besteffort. It uses the clusters named 'c1' and 'c2' for the project 'whisper' with the duration
defined by 'walltime'. In the prologue, we retrieve script and the parameter file on iRODS. 
One can add other parameters for each clusters such that the maximum number of
jobs runing at the same time (the variable 'max\_jobs').

@@

>>>>

%\end{multicols}
\begin{center}
\centering
\captionof{figure}[h]{\label{whisperCorrelationStep} Step of the correlations}
\includegraphics[width=6cm]{schemaCorrelationStep.png}
\end{center}
%\begin{multicols}{2}

@@

Whisper is one of the projects that have made it possible to ensure that the seismic noise brought new observable.
This permits to carry out several scientific results including imaging and monitoring. 
Concerning monitoring, further studies provide news results about sligth variations of seismics waves induce by earthquakes.
Many articles are in part due to this project as well as
several post-docs and PhD (see \cite{key:CFLC2010, key:BPCPBR, key:HCM2014, key:OPLC2013, key:PCP, key:MPPVCS}) and also whisper.obs.ujf-grenoble.fr, rubric publication).

@@

Schematically, the 'Main' Python module of IT code looks like:

\begin{lstlisting}
...
get parameter
...
build the iget commands
perform iget (encapsulation)
...
Codes whisper 
for seismogram processing 
....
build the iput commands
perform iput (encapsulation)
...

\end{lstlisting}

@@

For each of the 1280 jobs, a script is launched by CiGri , say 'start.bash', that take for
arguments a line of the file parameter. The script, among other things, load necessary library like appropriate python,
here 'main.py' and run the code (This is a diagrammatic view).

@@

#!/bin/bash
set -e
...
module load python
...
NumberDate=$2
IndexDate=$3
NumberStation=$4
IndexStation=$5
...
cd DirToCompute/Codes
python main.py NumberDate 
     IndexDate NumberStation IndexStation
...
cd
rm -rf DirToCompute
\end{lstlisting}

@@

"clusters": {

"c1": {
  "prologue": [
  secure_iget -f /IrodsColl/start.bash,
  secure_iget -f /IrodsColl/param.txt,
  mkdir -p DirToCompute,
  secure_iget -rf Codes DirToCompute,
  ... other lines of commands ],
  "project": "whisper",
  "walltime": "00:20:00"
  },

"c2": {
  "prologue": [
  ... lines of commands ],
  "project": "whisper",
  "max_jobs": "450",
  "walltime": "00:30:00"
  },
...
}
...
}
\end{lstlisting}

Here the campaign named 'test\_processing' take only one core. It run the file 'start.bash' with the parameter
file 'param.txt' in mode besteffort. It uses the clusters named 'c1' and 'c2' for the project 'whisper' with the duration
defined by 'walltime'. In the prologue, we retrieve script and the parameter file on iRODS as well as the code 'Codes' on iRODS. 
One can add other parameters for each clusters such that the maximum number of
jobs runing at the same time (the variable 'max\_jobs').

@@

\bibitem{key:MPPVCS}
Macquet M., Paul A., Pedersen H., Villase~nor A., Chevrot S., Sylvander M. and the PYROPE working group.
Ambient noise tomography of the Pyrenees and surrounding regions : inversion for a 3-D Vs model in a very heterogeneous crust.
{\em accepted in Geophysical Journal International.}
